\chapter*{General Introduction}
In today’s fast-evolving technological landscape, businesses increasingly need to leverage multiple cloud service providers to maintain flexibility, reduce costs, and avoid vendor lock-in. This shift has significantly increased the operational complexity of managing resources and services across various cloud platforms. As a result, the demand for a unified management solution has become more critical for companies aiming to streamline their operations and optimize their IT infrastructure.

Ilef Export, a prominent player in Tunisia's agricultural export industry, recognizes the strategic importance of integrating advanced IT solutions to enhance operational efficiency and competitiveness. To support this vision, Ilef Export is establishing a robust IT department to drive innovation and support the company’s growth objectives. My final year project aligns with this initiative, aiming to develop a unified platform that efficiently manages resources and services across multiple cloud providers, including AWS, Google Cloud, and Azure.

The project's primary goal is to design and implement a comprehensive solution that addresses the challenges of multi-cloud management. This involves overcoming operational complexities, mitigating the risks of vendor lock-in, and optimizing cost management. The platform will facilitate the creation of Docker images, deploying them to a private registry, and subsequently deploying them to a server. Additionally, integrating a Nexus repository registry will enhance artifact management within the development lifecycle.

This project aims not only to provide Ilef Export with state-of-the-art IT infrastructure but also to lay the foundation for future technological advancements. By successfully completing this project, Ilef Export will be well-positioned to harness the full potential of cloud technologies, driving innovation, improving productivity, and ensuring sustainable growth in the competitive agricultural export market.

The following sections of this report will delve into the detailed methodologies, design considerations, implementation strategies, and the results of this project. This comprehensive exploration aims to demonstrate how the proposed unified platform can address the outlined challenges and objectives effectively.